On Secure Delegation of SampBQP with a Classical Client

### 2020-01-18 qpip0.tex
Start typesetting parallelrep lemma

@@

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
	\end{itemize}
\end{theorem}

\Ethan{Maybe wrap the below into a protocol?}

Let $\varepsilon>0$. Pick $N$ large enough so that by

We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.

\Ethan{TODO analyze that the above actually works?}

>>>>

\subsection{Subprotocol for Quantum Measurements}

@@

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round".
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
		\item This is a 4-round protocol. The prover does not know whether it is a test or Hadamard round until the end of 3rd round.
		\begin{enumerate}
			\item The verifier generates $(k, td)$, ``key" and ``trapdoor". It sends the key to the prover.
			\item The prover computes a classical ``commitment" $y$ and sends it to the verifier.
			\item The verifier sends $c\in\set{0, 1}$, where $c=0$ corresponds to test round and $c=1$ corresponds to Hadamard round.
			\item The prover computes and sends a classical string $a$
		\end{enumerate}
	\end{itemize}
\end{theorem}

\subsection{Parallel Repetition of the Measurement Subprotocol}

Here we follow \cite{parallelrep}.

We characterize a prover by two unitaries $(U_0, U)$ acting on the space $\cH_C\otimes\cH_X\otimes\cH_Z\otimes\cH_Y\otimes\cH_K$.

\Ethan{I'll elaborate on above later, after figuring out exactly what I need or don't need}

Each coordinate can be accepted and rejected separately, and the entire protocol accepts only if all coordinates accept.

Let $A_{k_i, y_i}$ be the set of $a_i$s accepted by the verifier in the test round when the first and second messages are $k_i$ and $y_i$, respectively.

We present a lemma from \cite{parallelrep}.

\begin{lem}
	Let $(U_0, U)$ be some prover's strategy.
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\phi}_{X, Z}$,

	$$TODO-LONG-EQ$$

	where $t$ is the number of qubits in the register $ph$, $z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\phi_0}_{X, Z}$, $\ket{\phi_1}_{X, Z}$, $\ket{\phi_{err}}_{X, Z}$ may depend on $\gamma$.
	Furthermore, the following properties are satisfied.
	\begin{itemize}
		\item property 1
		\item property 1
		\item property 1
		\item property 1
		\item property 1
	\end{itemize}
\end{lem}
